JLyrics

### 2014-08-03 report/paper.tex
Finished conclusion.

\pdfmapline{=unisong@Unicode@ <ipam.ttf}
\begin{document}\sloppy % sloppy necessary here
\begin{CJK}{UTF8}{zhsong}
\title{JLyrics
    \titlenote{Submitted as the final project for CS 410 Summer 2014.}
}

@@

Our project was chosen to solve certain problems we had noticed in terms of information retrieval. For starters, looking up what song had a particular set of lyrics would not necessarily bring you to the same website storing those lyrics as another website also storing song lyrics. The information we want is sparsely distributed and uploaded. For example, if you do not know if the song originated from an anime or from a video game, you would not know whether to search an anime songs website or a video game songs website for the song. We wanted to combine the information sets of both or multiple websites so that you could be sure to run into the song you want to find.

@@

Here's why our project is great, and this is what we told you in the paper.

@@

>>>>

\pdfmapline{=unisong@Unicode@ <ipam.ttf}
\begin{document}\sloppy % sloppy necessary here
\begin{CJK}{UTF8}{zhsong}
\title{JLyrics}

@@

JLyrics is the name we gave our final project for CS 410. Our project was chosen to solve certain problems we had noticed in terms of information retrieval. For starters, looking up what song had a particular set of lyrics would not necessarily bring you to the same website storing those lyrics as another website also storing song lyrics. The information we want is sparsely distributed and uploaded. For example, if you do not know if the song originated from an anime or from a video game, you would not know whether to search an anime songs website or a video game songs website for the song. We wanted to combine the information sets of both or multiple websites so that you could be sure to run into the song you want to find.

@@

@@

Our project successfully indexes and searches a large database of Japanese songs. While it is regrettable that we could not also get to the Touhou Doujin CD site, we were able to get most of Piapro and all of Anime Lyrics dot Com's Japanese lyrics into the index. That is to say, this project is scalable to larger data sets. We have seen that for each of these sites, crawlers had to be adapted to retrieve the required lyrics from them. After crawling, it was necessary to generate readable documents to be indexed via parsing. After finally getting all 127,000 of the documents, we ran the Goose indexer on the data set with a Japanese Analyzer. Lastly, we performed search tests. While there were limitations on its efficacy, we could show that the searching worked reasonably well. We also discussed possibilities of expansion, whether with larger data sets, capability, or user-friendliness.
